Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-05 creep_beamer.tex
Fiber bundle model Jagla

\end{loglogaxis}
\end{tikzpicture}
\[ \sigma \propto  \gamma f^\alpha \xrightarrow{\mathrm{Fourier}} \sigma \propto \gamma t^{-\alpha} \]
Constant $\sigma$
\[ \gamma(t) \propto \sigma t^{\alpha} \xrightarrow{\frac{d}{dt}} \dot\gamma(t) \propto \sigma t^{\alpha-1}\]

@@

\begin{frame}{What about theories and models?}
\begin{columns}
\column{0.35\textwidth}
\structure{Fibre bundle model~\#1}

\textit{\footnotesize Jagla et al., PRE 2011}

@@

\begin{itemize}
\item elastic fibres
\item local yield strain
\item local coupling
\end{itemize}

%\hspace{1em}\includegraphics[width=\textwidth-1em]{Jagla_2011_gamma}

\column{0.35\textwidth}
\includegraphics[width=\textwidth, clip=true, trim=0 0 0 10cm]{MEB_cas4_gdl1_22}
\end{columns}
predicts Andrade creep and failure \alert{but} critical stress $\tau_f\sim\left(\sigma-\alert{\sigma_c}\right)^{-1.25}$
\end{frame}

>>>>

\end{loglogaxis}
\end{tikzpicture}
\[ \boxed{\sigma \propto  \gamma f^\alpha} \xrightarrow{\mathrm{Fourier}} \boxed{\sigma \propto \gamma t^{-\alpha}} \]
Constant $\sigma$
\[ \boxed{\gamma(t) \propto \sigma t^{\alpha}} \xrightarrow{\frac{d}{dt}} \boxed{\dot\gamma(t) \propto \sigma t^{\alpha-1}}\]

@@

\begin{frame}{Fibre bundle models}
\tikzsetnextfilename{FBM_Jagla}
\begin{tikzpicture}
\let\mydima\relax
\newlength\mydima
\setlength{\mydima}{0.3\textwidth}
\let\mydimb\relax
\newlength\mydimb
\setlength{\mydimb}{2\baselineskip}

\node[fill=black, inner sep=0, minimum height=0.2em, minimum width=\mydima] at (0,\mydimb)  (top) {};
\node[fill=black, inner sep=0, minimum height=0.2em, minimum width=\mydima] at (0,-\mydimb)  (bot) {};

\foreach \x in {0.1,0.2,...,0.9}\draw[Accent1, line width=0.1em*sin(1500*\x)+0.3em] (top.south west) ++(\x\mydima, 0) -- +(0, -2\mydimb+0.2em);

\node[above=0 of top, single arrow, draw, shape border rotate=90] {$\sigma$};
\node[starburst, draw=Accent2, inner sep=0pt,  minimum width=0.1\mydima, minimum height=0.5\mydimb, starburst point height=0.15em] at (-0.1\mydima,0) {};
\node[double arrow,draw, anchor=west, text width=0.21\textwidth, align=center] at (0.5\mydima,-0.5\mydimb) (model) {\structure{model}};
\node[above left=\baselineskip and 0of model.east, text width=0.31\textwidth, inner sep=0] {\begin{itemize}
	\item elastic fibres
	\item local yield strain
	\item local coupling
	\end{itemize}};
\end{tikzpicture}
\includegraphics[height=6\baselineskip, clip=true, trim=0 0 0 10cm]{MEB_cas4_gdl1_22}

\bigskip
\begin{columns}[b]
\column{0.3\textwidth}
\textit{\footnotesize Jagla et al., PRE 2011}

@@

\column{0.3\textwidth}
\structure{But}
\begin{itemize}
\item yield stress
\item built in power-law creep
\item no master curve
\end{itemize}

\column{0.4\textwidth}\tikzsetnextfilename{creep_1_3}
\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 2,
			vertical sep=2.5em,
			},
		height=6.5\baselineskip,
		width=9\baselineskip,
		cycle list name=earthy,
		clip mode=individual,
		ylabel={$\dot{\gamma}/\dot{\gamma}_\text{min}$},
		xlabel shift=-0.5em,
		]
	\nextgroupplot[
		xmin=1e-5, xmax=2, xlabel={$t/\tau_f$},
		xmode=log,ymode=log,
		xtick={1e-4, 1e-2, 1},
		]
		\addplot table[x index=1, y index=3]{Y27_200Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y38_300Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y25_400Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y32_550Pa_gdot_decimated.txt};
		\addplot table[x index=1, y index=3]{Y39_1000Pa_gdot_decimated.txt};
		\addplot[yellow, ultra thick, samples at={1e-5,1e-4, 1e-3,1e-2,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9, 0.99, 0.999, 0.9999, 0.99999}] {0.378*x^(-0.85) + 0.187/(1-x)};

	\nextgroupplot[
		xmin=1e-5, xmax=2, xlabel={$(\tau_f-t)/\tau_f$},
		x dir=reverse,
		xmode=log,ymode=log,
		xtick={1e-4, 1e-2, 1},
	]
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y27_200Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y38_300Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y25_400Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y32_550Pa_gdot_decimated.txt};
		\addplot table[x expr=1-\thisrowno{1}, y index=3]{Y39_1000Pa_gdot_decimated.txt};
		\addplot[yellow, ultra thick, samples at={1e-5,1e-4, 1e-3,1e-2,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9, 0.99, 0.999, 0.9999, 0.99999}] {0.378*(1-x)^(-0.85) + 0.187/x};
	\end{groupplot}
\end{tikzpicture}
\end{columns}
\end{frame}
